|

### 2024-05-10 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Change needed for the Multispecies forward simulations

# Now do the same with the differences
comp.lam.diff.res <- do.call('rbind',comp.lam.diff)
# I want to turn this into a table....
comp.lam.diff.res.tab <- comp.lam.diff.res
# Round the numbers
comp.lam.diff.res.tab$min.abund <- round(comp.lam.diff.res.tab$min.abund,digits=2)
rounders <- c("lam.fish.min.40","lam.fish.min.max","lam.fish.40.max",
                    "lam.nf.min.40","lam.nf.min.max","lam.nf.40.max")
comp.lam.diff.res.tab[,rounders] <- round(comp.lam.diff.res.tab[,rounders] ,digits=3)
# Now give it pretty names
tab.names <- c("Minimum Abundance",
               "$\\lambda_{F>0}^{Min-40}$",
               "$\\lambda_{F>0}^{Min-Max}$",
               "$\\lambda_{F>0}^{40-Min}$",
               "$\\lambda_{F=0}^{Min-40}$",
               "$\\lambda_{F=0}^{Min-Max}$",
               "$\\lambda_{F=0}^{40-Max}$",
               "Stock","Species")
names(comp.lam.diff.res.tab) <- tab.names

>>>>

# Now do the same with the differences
comp.lam.diff.res <- do.call('rbind',comp.lam.diff)
# I want to turn this into a table....
comp.lam.diff.res.tab <- comp.lam.diff.res
# Round the numbers
comp.lam.diff.res.tab$min.abund <- round(comp.lam.diff.res.tab$min.abund,digits=2)
rounders <- c("lam.fish.min.40","lam.fish.min.max","lam.fish.40.max",
                    "lam.nf.min.40","lam.nf.min.max","lam.nf.40.max")
comp.lam.diff.res.tab[,rounders] <- round(comp.lam.diff.res.tab[,rounders] ,digits=3)
# Now give it pretty names
tab.names <- c("Minimum Abundance",
               "$\\lambda_{F>0}^{Min-40}$",
               "$\\lambda_{F>0}^{Min-Max}$",
               "$\\lambda_{F>0}^{40-Max}$",
               "$\\lambda_{F=0}^{Min-40}$",
               "$\\lambda_{F=0}^{Min-Max}$",
               "$\\lambda_{F=0}^{40-Max}$",
               "Stock","Species")
names(comp.lam.diff.res.tab) <- tab.names
